---
title: "Assignment 3 Q 2"
author: "Zhang HeXiao"
date: "2020/3/5"
output:
  html_document:
    df_print: paged
---
This simple example explains why cross-validation is important in variable selection.

### Data Preparation

The set of data is about the deals of real estate in a certain place,
and we try to fit a linear model to predict the price of real estate.

Note that the predictor 'ID' actually has nothing to do with the price.

```{r}
rm(list=ls())
library(dplyr)

# Data taken from "http://www.stat.cmu.edu/~cshalizi/mreg/15/hw/08/real-estate.csv"
real.estate <- read.csv("./real-estate.csv")
head(real.estate)
```

### Variable Selection without Cross-Validation

The performance of the model seemed to degrade when we just dropped 'ID' without cross-validation.

That's certainly not because 'ID' was predictive, but because our model was overfitting.

```{r}
# begin with a full model
lm.all <- lm(Price~., data=real.estate)

# try to remove the insignificant prodictor 'ID'
lm.no.ID <- lm(Price~.-ID, data=real.estate)

cat("---------- Variable Selection without Cross Validation ----------\n")
cat("The MSE of the model with 'ID' is", mean(lm.all$residuals^2), "\n")
cat("The MSE of the model without 'ID' is", mean(lm.no.ID$residuals^2), "\n")
```

### Variable Selection with Cross-Validation

With K-Fold Cross Validation, we got an ideal result.

```{r}
# K-Fold CV
set.seed(20200305)
K <- 5
N <- nrow(real.estate)
train.id <- rep(1:K, length.out=N) %>% sample(N)
Err.all <- rep(0, K)
Err.no.ID <- rep(0,K)
for(k in 1:K){
  training.set <- real.estate[train.id!=k,]
  test.set <- real.estate[train.id==k,]
  
  lm.all.cv <- lm(Price~., data=training.set)
  lm.no.ID.cv <- lm(Price~.-ID, data=training.set)
  Err.all[k] <-  mean((test.set$Price -
                         predict(lm.all.cv, test.set))^2)
  Err.no.ID[k] <- mean((test.set$Price -
                          predict(lm.no.ID.cv, test.set))^2)
}

cat("---------- Variable Selection with Cross Validation ----------\n")
cat("The MSE of the model with 'ID' is", mean(Err.all), "\n")
cat("The MSE of the model without 'ID' is", mean(Err.no.ID), "\n")
```
